Deep Reinforcement Learning for Conservation Decisions

### 2021-10-15 manuscript/manuscript.Rmd
Adding line nos and dbl spacing

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala, @hafner_learning_2019, @weber_imagination-augmented_2018
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
#  - \usepackage{lineno}
#  - \usepackage{endfloat}
#  - \linenumbers

>>>>

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala, @hafner_learning_2019, @weber_imagination-augmented_2018
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{setspace}
  - \usepackage{lineno}
#  - \usepackage{endfloat}
  - \linenumbers
  - \doublespacing
